\thetitle

### 2013-04-18 tfpie/tfpie.tex
finish related work

\cite{dvanhorn:Allen2002DrJava, dvanhorn:Hsia2005Taming}

\cite{dvanhorn:Kolling2003}

\cite{dvanhorn:Bruce2001Library}

\cite{dvanhorn:Alphonce2003Using}

>>>>

The problems of teaching Java in introductory courses have been
well-explored; we mention only a few related directions here.
DrJava~\cite{dvanhorn:Allen2002DrJava} and
BlueJ~\cite{dvanhorn:Hsia2005Taming,dvanhorn:Kolling2003} are
introductory environments for Java, which alleviate some but not all
of the drawbacks we have outlined.
%
Several teaching-oriented graphics libraries for Java have been
proposed~\cite{dvanhorn:Bruce2001Library,dvanhorn:Alphonce2003Using},
but these are significantly more complex than the graphics and
interaction libraries we are able to use in the introductory language
we present.
